Interpretable Machine Learning

### 2017-11-22 talk.Rmd
change order, continue slides

@@

## When is it important

## Different entry points
- Understand data better
- Use only interpretable models (sparse linear models, short decision trees, rules, ...)
- **Apply model-agnostic methods to make black boxes interpretable**

@@

## Predicting house prices
TODO: Add example dataset

## PDP

>>>>

Machine learning is a method for teaching computers to make and improve predictions or behaviours based on data.

# Let's predict data scientist salaries

## Step 1: Find a problem
Hypothetical scenario: For a customer, an HR company, we want to predict data scientist salaries.

## Step 2: Find some data
Kaggle conducted an industry-wide survey of data scientists. 
Questions asked: 
- Demographic
- Salary
- Are you currently enrolled as a student at a degree granting school?	
- How adequately do you feel your title describes what you do (or what you did if retired)?	
- How long have you been learning data science?	
TODO: Add only relevant questions here for analysis

```{r load-data, warning=FALSE, include=FALSE}
library('mlr')
library('ggplot2')
source('code/prepare-kaggle-data.R')
```

## Step 3: Throw ML on your data
```{r learn}
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
n = getTaskSize(task)
lrn = makeLearner('regr.randomForest')
mod = train(lrn, task, subset = seq(1, n, 2))
pred = predict(mod, task = task, subset = seq(2, n, 2))
## TODO: Find better variables https://www.kaggle.com/kaggle/kaggle-survey-2017/data
performance(pred, measures = list('mae'=mae))
```
## We are done! {.center}

```{r, echo=FALSE}
knitr::include_graphics("images/done-here.gif")
```

@@

## When is it important
http://people.dbmi.columbia.edu/noemie/papers/15kdd.pdf
Asthma example

## Different entry points
- Understand data better $\rightarrow$ do it!
- Use only interpretable models (sparse linear models, short decision trees, rules, ...) $\rightarrow$ does not always work. 
- **Apply model-agnostic methods to make black boxes interpretable** $\rightarrow$ cool, tell me more

@@

## Partial dependence plots
TODO: Fix Tenure variable ordering
TODO: Rotate labels
```{r}
pdp1 = generatePartialDependenceData(mod, task, features =c('Tenure'))
ggplot(pdp1$data) + geom_point(aes(x=Tenure, y=CompensationAmount)) + 
  scale_y_continuous(limits=c(0, NA))
```

## By age

```{r}
pdp1 = generatePartialDependenceData(mod, task, features =c('Age'))
plotPartialDependence(pdp1) + scale_y_continuous(limits = c(0, NA))
```

## By education

```{r}
pdp1 = generatePartialDependenceData(mod, task, features =c('FormalEducation'))
plotPartialDependence(pdp1) + scale_y_continuous(limits = c(0, NA))
```
